---
title: "Week 05: World Data Investigation"
author: "Polisma Yadav"
date: "10/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Notes

·       Add Labels with labs() function

·       Eg:

ggplot(mpg, aes(displ, hwy)) +

  geom_point(aes(color = class)) +

  geom_smooth(se = FALSE) +

·       labs(title = "Fuel efficiency generally decreases with engine size")

·       Can also add subtitle and caption, just use those words instead of or with title

·       Can also be used to replace short variables on x-axis and y-axis with more detailed descriptions. Use X/Y instead of title

·       Incase you need to use mathematical equation instead of string, use quote() within labs ()

·       There are two main ways to get your plots out of R and into your final write-up: ggsave() and knitr. ggsave() will save the most recent plot to disk:

ggplot(mpg, aes(displ, hwy)) + geom_point()

```{r}
library(tidyverse)
install.packages("devtools")
library(devtools)
devtools::install_github("drsimonj/ourworldindata")
child_mortality_rate <- ourworldindata::child_mortality
child_mortality_rate
```


```{r}
library(mosaic)
child_mortality_rate2 <- filter(child_mortality_rate, year == "2010" )
```

```{r}
child_mortality_rate3 <- filter(child_mortality_rate2, population >= 126535920) 
View(child_mortality_rate3)

```

```{r}
child_mortality_rate3 %>% 
  arrange(country)
View(child_mortality_rate3)
```

```{r}
child_mortality_rate3 %>% 
  summarise(aveMortlaity = mean(child_mort))
```

```{r}
library(ggplot2)
ggplot(child_mortality_rate3, aes(x=child_mort, y=deaths_per_woman)) +
  geom_point(size = 6, color = "red", pch = 18) +
  labs(title="Child mortality rate compared to deaths per woman of top 10 most populated countries in the world", 
       x = "child mortality rate", y="deaths per woman") +
  theme_bw()
```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
